Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2021-02-19 eg6-letters/long-paper/prc-dvcshelium.tex
Changes for PRC submission

\begin{figure}[tbp!]
\center
\includegraphics[width=10.0cm]{fig1/GPD.png}
\caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
	Single lines can represent quarks or anti-quarks probed in the nucleon shown by the triple lines.}
\label{fig:GPD}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig1/finalplane.png}
	\caption{Illustration of the scattering (or leptonic) and production (or hadronic) planes
	in the DVCS process.} 
\label{fig:PhiAngle}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
\caption{Diagram representing the coherent nuclear DVCS, where we 
indicate the limit between the hard and the soft components with the dot-dashed factorization line.}
\label{fig:CohDiag}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{fig3/AlphaCoefs.png}
	\caption{Coefficients presented in Eqs. \ref{eq:alpha1} to \ref{eq:alpha4}.
	Note the prescaling factors used for $\alpha_0$, $\alpha_2$ and $\alpha_3$.}
\label{fig:alphas}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/handbag_incoherent.pdf}
\caption{Diagram representing the incoherent nuclear DVCS.}
\label{fig:InCohDiag}
\end{figure}

@@

\begin{figure}[tbp!]
\center
	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
	\caption{The $\sin(\phi)$ moment of the BSA as a function of $-t$ measured by HERMES
	for a series of nuclei \cite{Airapetian:2009cga}. The gray bands represent the systematic 
        uncertainties.}
\label{fig:HERMES1}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
\caption{The $\sin(\phi)$ moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
the outer represent the quadratic sum of the statistical and systematic uncertainties.}
\label{fig:HERMES2}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{fig3/CLAS_geantview-PS.jpg}
	\caption{View of the CLAS detector setup.}
\label{fig:CLAS}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{fig3/IC-CLAS.png}
	\caption{Representation of the inner calorimeter (IC) of CLAS. The crystals that compose the
	sensitive part of the detector are represented in purple.}
\label{fig:IC}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{fig3/solenoid.png}
\caption{Representation of the center of CLAS with the beam background in red with and without
	the solenoid field activated, right and left, respectively.}
\label{fig:Solenoid}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/RTPC_new_1.png}
\caption{Cut view of the RTPC.}
\label{fig:RTPCGlobal}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[trim=10 10 10 5,clip,width=16.5cm]{fig3/all_coh_exc_cuts.png}
        \caption{Distributions of the coherent photon production events before 
        (blue) and after (black line filled
	in gray) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$ components, in order left to right and top to bottom. 
	}
\label{fig:CohExcCuts}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[trim=10 10 10 
   5,clip,width=16.5cm]{fig3/all_incoh_exc_cuts.png}
\caption{Distributions of the incoherent photon production events before (blue) 
   and after (black line filled
	in gray) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$ components, in order left to right and top to bottom.}
\label{fig:IncExcCuts}
\end{figure}

@@

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/xB_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/Q2_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/t_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/phi_h_Coh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	coherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
\label{fig:CohPi0Simul}
\end{figure}

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/xB_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/Q2_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/t_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/phi_h_InCoh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	incoherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
\label{fig:InCohPi0Simul}
\end{figure}

@@

\begin{figure}[tbp]
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The estimated coherent (left) and incoherent (right) $\pi^{0}$ 
contamination fraction in the DVCS events as a function of the 
transferred momentum squared -$t$ and integrated over the kinematic 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=15cm]{fig3/t_tprime_ALU_90_p_shortscenrario.pdf}
	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
	function of $Q^2$, $x_{B}$ and $-t$, using the photon based $t$ definition (red)
	and the proton based $t^\prime$ definition (black).}
\label{fig:ttpComp}
\end{figure}

@@

\begin{figure}[bp!]
\center
\includegraphics[width=12cm]{fig3/Coherent_ALU_phi.pdf}
	\caption{The BSA in the coherent exclusive photo-production off helium-4 as a 
	function of $\phi$ and $Q^2$ 
	(top panels), $x$ (middle panels) and $-t$ (lower panels). The error bars are  
	statistical and the gray bands represent the systematic uncertainties. The full red lines show
	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
\label{fig:CohALUphi}
\end{figure}

\begin{figure}[tbp]
\center
\includegraphics[width=16cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles~\cite{Airapetian:2009cga}. The theoretical prediction 
	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta dashed line.}
\label{fig:CohALU90}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{fig3/Coherent_CFF.pdf}
	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
	$-t$ (right panels). The red full line is the theoretical calculation by 
	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
	the blue long dashed line shows the predictions by Liuti {\it et 
	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
\label{fig:CohCFF}
\end{figure}

@@

\begin{figure}[bp!]
\center
\includegraphics[width=15cm]{fig3/incoherent_ALU_phi.pdf}
	\caption{The BSA in the incoherent exclusive photo-production off a proton bound in
	helium-4 as a function of $\phi$ and $Q^2$ 
	(top panels), $x$ (middle panels) and $-t$ (lower panels). The error bars are  
	statistical and the gray bands represent the systematic uncertainties. The data is fitted with the 
	form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$; the results of the 
	fits are drawn with black full lines.}
\label{fig:InCohALUphi}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line, and 
	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}

>>>>

\begin{figure}[tbp!]
\center
\includegraphics[width=10.0cm]{GPD.png}
\caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
	Single lines can represent quarks or anti-quarks probed in the nucleon shown by the triple lines.}
\label{fig:GPD}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{finalplane.png}
	\caption{Illustration of the scattering (or leptonic) and production (or hadronic) planes
	in the DVCS process.} 
\label{fig:PhiAngle}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{DVCS_diagram.pdf}
\caption{Diagram representing the coherent nuclear DVCS, where we 
indicate the limit between the hard and the soft components with the dot-dashed factorization line.}
\label{fig:CohDiag}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{AlphaCoefs.png}
	\caption{Coefficients presented in Eqs. \ref{eq:alpha1} to \ref{eq:alpha4}.
	Note the prescaling factors used for $\alpha_0$, $\alpha_2$ and $\alpha_3$.}
\label{fig:alphas}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{handbag_incoherent.pdf}
\caption{Diagram representing the incoherent nuclear DVCS.}
\label{fig:InCohDiag}
\end{figure}

@@

\begin{figure}[tbp!]
\center
	\includegraphics[width=10.5cm]{HERMES_BSA.png}
	\caption{The $\sin(\phi)$ moment of the BSA as a function of $-t$ measured by HERMES
	for a series of nuclei \cite{Airapetian:2009cga}. The gray bands represent the systematic 
        uncertainties.}
\label{fig:HERMES1}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{HERMES_BSA_2.png}
\caption{The $\sin(\phi)$ moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
the outer represent the quadratic sum of the statistical and systematic uncertainties.}
\label{fig:HERMES2}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{CLAS_geantview-PS.jpg}
	\caption{View of the CLAS detector setup.}
\label{fig:CLAS}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=8cm]{IC-CLAS.png}
	\caption{Representation of the inner calorimeter (IC) of CLAS. The crystals that compose the
	sensitive part of the detector are represented in purple.}
\label{fig:IC}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{solenoid.png}
\caption{Representation of the center of CLAS with the beam background in red with and without
	the solenoid field activated, right and left, respectively.}
\label{fig:Solenoid}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{RTPC_new_1.png}
\caption{Cut view of the RTPC.}
\label{fig:RTPCGlobal}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[trim=10 10 10 5,clip,width=16.5cm]{all_coh_exc_cuts.png}
        \caption{Distributions of the coherent photon production events before 
        (blue) and after (black line filled
	in gray) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$ components, in order left to right and top to bottom. 
	}
\label{fig:CohExcCuts}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[trim=10 10 10 
   5,clip,width=16.5cm]{all_incoh_exc_cuts.png}
\caption{Distributions of the incoherent photon production events before (blue) 
   and after (black line filled
	in gray) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$ components, in order left to right and top to bottom.}
\label{fig:IncExcCuts}
\end{figure}

@@

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_Coh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_Coh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	coherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
\label{fig:CohPi0Simul}
\end{figure}

\begin{figure}[p]
\center
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_InCoh_pi0.png}
\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_InCoh_pi0.png}
	\caption{The measured (filled blue) and simulated (red) distributions of
	incoherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
\label{fig:InCohPi0Simul}
\end{figure}

@@

\begin{figure}[tbp]
\includegraphics[width=8cm]{T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The estimated coherent (left) and incoherent (right) $\pi^{0}$ 
contamination fraction in the DVCS events as a function of the 
transferred momentum squared -$t$ and integrated over the kinematic 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=15cm]{t_tprime_ALU_90_p_shortscenrario.pdf}
	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
	function of $Q^2$, $x_{B}$ and $-t$, using the photon based $t$ definition (red)
	and the proton based $t^\prime$ definition (black).}
\label{fig:ttpComp}
\end{figure}

@@

\begin{figure}[bp!]
\center
\includegraphics[width=12cm]{Coherent_ALU_phi.pdf}
	\caption{The BSA in the coherent exclusive photo-production off helium-4 as a 
	function of $\phi$ and $Q^2$ 
	(top panels), $x$ (middle panels) and $-t$ (lower panels). The error bars are  
	statistical and the gray bands represent the systematic uncertainties. The full red lines show
	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
\label{fig:CohALUphi}
\end{figure}

\begin{figure}[tbp]
\center
\includegraphics[width=16cm]{Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles~\cite{Airapetian:2009cga}. The theoretical prediction 
	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta dashed line.}
\label{fig:CohALU90}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=14cm]{Coherent_CFF.pdf}
	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
	$-t$ (right panels). The red full line is the theoretical calculation by 
	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
	the blue long dashed line shows the predictions by Liuti {\it et 
	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
\label{fig:CohCFF}
\end{figure}

@@

\begin{figure}[bp!]
\center
\includegraphics[width=15cm]{incoherent_ALU_phi.pdf}
	\caption{The BSA in the incoherent exclusive photo-production off a proton bound in
	helium-4 as a function of $\phi$ and $Q^2$ 
	(top panels), $x$ (middle panels) and $-t$ (lower panels). The error bars are  
	statistical and the gray bands represent the systematic uncertainties. The data is fitted with the 
	form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$; the results of the 
	fits are drawn with black full lines.}
\label{fig:InCohALUphi}
\end{figure}

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_90_p_vs_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_90_p_vs_x_shortscenrario.pdf}
	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line.}
\label{fig:IncALU}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
	by the full blue line, the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line, and 
	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}
